Staged Abstract Interpreters

### 2019-02-12 paper/10_intro.tex
code & revision

Now we have seen two orthogonal transformations of interpreters: by
speclization, we can refactor interpreters to compilers; by abstraction, we can
refactor interpreters to static analyzers. As an intellectual quest, it is
natural to ask, starting from an interpreter, can we derive sound abstract
interpreters but it works like a compiler and generates fast analysis code?

@@

Besides the intellectual merit of the confluence diagram, this paper contributes
to a practical problem in static analysis: can we speed up a static analyzer
without any intrusive changes and soundness compromises?

>>>>

Now we have seen two orthogonal transformations of interpreters: by
speclization, we can refactor interpreters to compilers; by abstraction, we can
refactor interpreters to static analyzers. As an intellectual quest, it is
natural to ask --- starting from an interpreter, can we derive sound abstract
interpreters but it works like a compiler and generates fast analysis code?

@@

Besides the intellectual merit of the confluence diagram, this paper contributes
to a practical problem in static analysis: can we speed up a static analyzer
without any intrusive changes and soundness compromises?
\todo{specializing analysis wrt program is not new; first staging; we argue that
staging is less intrusive compared with AC (ie, closure generation), in
fact,LMS-based staging only requires type annotations }
